Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-02 p2/p2.Rmd
rearranging files

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

\hh{'considered to be unique' by AFTE - that is right, but we should not use this argument, and I don't think we have to. It's better to focus on the problem at hand: striation marks are used to determine same source for bullets. XXX we could include some figures here XXX Current standards ask for a visual inspection of the marks under a comparison microscope by a firearms examiner. One of the problems raised by the NAS report in 2009 is the subjectivity involved in this comparison and the need for determining error rates \citep{NAS:2009}. There are different approaches used to achieve more objectivity and assess error rates. XXX here we need some examples of approaches XXX
For toolmarks, the Chumbley score has been suggested to determine same-source. XXX summary of results from original paper and the adjustment XXX
In this paper we are interested in how this method has to be adjusted to best be applied to the smaller marks on bullets. }
\gk{done}

@@

A maximum correlation statistic is used to identify the region of best agreement, with the maximum usually seen being near 1 for both cases which is what we intuitively expect for matches, and something which we do not intuitively expect for non matches \gk{done}\hh{XXX get rid of the parentheses - put the content into a sentence after your first statement.}

\hh{XXX the process you describe below is the cross-correlation of two series $x(t)$ and $y(t)$.}

First, there are a very large number of cross-correlations calculated for the two series of striae or marks $x(t_1)$ and $y(t_2)$, for eg if the window of optimization was defined as 200 and toolmark pixel length is around 1000 then we have 1200-(200-1) = 1001. Can be thought of ordered arrangements without replacement where n = 1001 and r = 1.

@@

```{r win-comparison, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap=" The two plots on the left show how the same shift behaves in case of a matching pair and the two plots on the right show how the different shift behaves in case of a matching pair."}
a<- matrix(NA, ncol = 3, nrow = 2)
toolmark.falsepositive<- data.frame(a)
colnames(toolmark.falsepositive)<- c("Classification", "Match", "Non-Match")
toolmark.falsepositive$Classification<- c("Match", "Non-Match")
toolmark.falsepositive$Match<- c(47,0)
toolmark.falsepositive$`Non-Match`<- c(3,50)
toolmark.falsepositive

@@

Let ns and nd be the number of same shift and different shift windows
$N = n_{s} + n_{d}$

The mann whitney U statistic is given by
$U =\sum^{ns}_{i=1}R_{s}\left( i\right)$

@@

$\overline{U}= \dfrac{U-M}{\sqrt{V}}$

@@

$M = n_{s}\left(\dfrac{N+1}{2}\right)$

@@

$V = \dfrac{n_{s}n_{d}}{N\left(N-1\right)}\left[\Sigma^{n_{s}}R_{s}\left(i\right)^{2}+\Sigma^{n_{d}}R_{d}\left(j\right)^{2}\right] -\dfrac{n_{s} n_{d}\left(N+1\right)^{2}}{4\left(N-1\right)}$

@@

<!-- \begin{minipage}{0.3\textwidth} -->
```{r }
library(kableExtra)
a27<- all %>% filter(wo==320, wv==50) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 320 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))

```
<!-- \end{minipage} -->
<!-- \begin{minipage}{0.3\textwidth} -->
```{r}
a27<- all %>% filter(wo==120, wv==50) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 120 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```
<!-- \end{minipage} -->
```{r}
a27<- all %>% filter(wo==80, wv==50) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 80 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

@@

knitr::kable(t(param_setting)[,17:33], digits=0, format = "latex" ,booktabs=TRUE) %>% kableExtra::kable_styling(latex_options = c("scale_down","hold"))

@@

```{r, fig.cap="Type II errors for different levels of coarseness. XXX We need more values around .25"}
errors2 %>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")
```

### comparison of total error with signatures and profiles

@@

errors_sig_c %>% ggplot(aes(x = coarse, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line() + geom_point(data=errors2, aes(shape="profiles")) +geom_line(data=errors2, aes(shape="profiles"))
```
## Discussion

>>>>

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

@@

A maximum correlation statistic is used to identify the region of best agreement, with the maximum usually seen being near 1 for both cases which is what we intuitively expect for matches, and something which we do not intuitively expect for non matches

First, there are a very large number of cross-correlations calculated for the two series of striae or marks $x(t_1)$ and $y(t_2)$, for eg if the window of optimization was defined as 200 and toolmark pixel length is around 1000 then we have 1200-(200-1) = 1001.

@@

```{r win-comparison, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap=" The two plots on the left show how the same shift behaves in case of a matching pair and the two plots on the right show how the different shift behaves in case of a matching pair."}
a<- matrix(NA, ncol = 3, nrow = 2)
toolmark.falsepositive<- data.frame(a)
colnames(toolmark.falsepositive)<- c("Classification", "Match", "Non-Match")
toolmark.falsepositive$Classification<- c("Match", "Non-Match")
toolmark.falsepositive$Match<- c(47,0)
toolmark.falsepositive$`Non-Match`<- c(3,50)

knitr::kable(toolmark.falsepositive, digits=0, format = "latex" ,booktabs=TRUE) %>% kableExtra::kable_styling(latex_options = c("hold"))

@@

Let ns and nd be the number of same shift and different shift windows
$$N = n_{s} + n_{d}$$

The mann whitney U statistic is given by
$$U =\sum^{ns}_{i=1}R_{s}\left( i\right)$$

@@

$$\overline{U}= \dfrac{U-M}{\sqrt{V}}$$

@@

$$M = n_{s}\left(\dfrac{N+1}{2}\right)$$

@@

$$V = \dfrac{n_{s}n_{d}}{N\left(N-1\right)}\left[\Sigma^{n_{s}}R_{s}\left(i\right)^{2}+\Sigma^{n_{d}}R_{d}\left(j\right)^{2}\right] -\dfrac{n_{s} n_{d}\left(N+1\right)^{2}}{4\left(N-1\right)}$$

@@

```{r }
library(kableExtra)
a27<- all %>% filter(wo==200, wv==30) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 320 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))

```{r}
a27<- all %>% filter(wo==120, wv==30) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 120 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

```{r}
a27<- all %>% filter(wo==80, wv==30) %>% xtabs(data= ., ~signif+match)
knitr::kable(a27, digits=0, caption = "Window of Optimization 80 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

@@

knitr::kable(t(param_setting)[,18:33], digits=0, format = "latex" ,booktabs=TRUE) %>% kableExtra::kable_styling(latex_options = c("scale_down","hold"))

@@

```{r, fig.cap="Type II errors for different levels of coarseness. XXX We need more values around .25"}
errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")
```

### Comparison of total error with signatures and profiles

@@

total1<- errors_sig_c %>% ggplot(aes(x = coarse, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line()  + geom_point(data= errors2 %>% filter(wv==30), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv==30), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("type I error"~alpha), palette="Set2")

total2<- wo120 %>% filter(wv>10) %>% ggplot(aes(x = wv, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line() +geom_point(data=errors2 %>% filter(wv>10) %>% filter(coarse==0.25), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv>10)%>% filter(coarse==0.25), aes(shape="profiles")) + theme_bw()

multiplot(total1, total2)
```
## Discussion
